Qualifying Examination Paper

### 2018-10-24 main.tex
181024-1943 sync

%\subsection{Introduction}
The Generative Adversarial Nets (GAN) framework was first introduced by Goodfellow et al. in 2014 \cite{NIPS2014_5423}.  The GAN framework involves the simultaneous training of both a generative model $G$ with parameters $\theta_g$ and a discriminative model $D$ with parameters $\theta_d$.  Given a target data space $T$ with distribution $p_t$, $G$'s task is to learn a mapping from an noisy input $z$ to the data space $p_t$ ($G:Z \rightarrow G(z) \sim p_g \approx p_t$); while $D$'s task is to discriminate whether some input $x$ originated from either $T$ or $G(z)$ ($D: X \rightarrow \{0, 1\}$).  Since $G$ would like to generate samples that are representative of $T$, and therefore make $D$'s task more difficult by capturing $p_t$ with $p_g$, $D$ includes a loss term that is based on whether $D$ successfully discriminated inputs as $T$ or $G(z)$ and back-propagates $D$'s success as error to $\theta_g$ appropriately.  In this way, $G$ learns how to generate data that is hard for an ever-improving $D$ to distinguish.  Importantly, labeled data is not required for either $G$ or $D$ because the loss function used by $G$ is defined in terms of $D(x)$ and $(1-D(G(z))) \in \{0, 1\}$ (ie. did $G$ fool $D$?) and the labels for $x$ essentially map to $\{p_t, p_g\}$ (ie. from target or generated data?).  Thus, the GAN framework presents a promising approach for generating data that approximates a target distribution in an unsupervised manner.

@@

In the original GAN, $G$ learns to generate data that estimates $p_t$, but cannot target specific sub-distributions within $p_t$, such as class labels or modes within $p_t$.  Shortly after the original GAN was introduced, Mirza and Osindero introduced an extension called Conditional GAN \cite{mirza2014conditional} which addresses this need.  By adding a conditioning input layer to both models $G$ and $D$, one can present the conditioning data $y$ alongside the normal data.  $G$ will learn a mapping from $z$ to $X$ given $y$ that will result in making classification of $X$ given $y$ difficult for $D$.  This advancement seems obvious in retrospect, but warrants contemplation.  While $G$ represents a mapping that captures the distribution of the target data space $T$ in general, the noisy input $z$ can be thought of as the diversity component of the input and the input $y$ can be thought of as the specification component of the input.  Since the $y$ specification value is consistent within modes, a smaller portion of the overall networks for $G$ and $D$ can focus on the generation and discrimination, respectively, of the modal contribution whereas the remaining portions of the networks can focus on the unspecified contributions from $z$.  Of course, Conditional GAN requires that conditioning data (eg. labels) is available for all target samples $x \in X$.

%(TBD) LAPGAN

As the appreciation and use of GAN-based approaches increased, it was observed that the structure design of the $G$ and $D$ models deserved reconsideration.  Radford, Metz, and Chintala \cite{DBLP:journals/corr/RadfordMC15} evaluated various model architectures and recommended a set of guidelines and constraints for $G$ and $D$ architectures that appeared to perform well in terms of stability, convergence, resolution, and depth of representation.  These guidelines describe a Deep Convolutional GAN (DCGAN) and are summarized as follows: (a) use convolution and fractional convolution layers with striding to achieve adaptive down-sampling ($D$) or up-sampling ($G$), respectively, rather than fixed/deterministic methods (i.e. max pooling), (b) use batch normalization between convolution layers to mitigate collapse or failure due to poor initialization or vanishing gradients, (c) avoid fully-connected layers, with the exception of the input to $G$ and the output of $D$, to help earlier convergence, and (d) use Rectifier Linear Unit (ReLU) activation for input and hidden layers in $G$, tanh for the output layer in $G$, and Leaky ReLU for all layers in $D$.  In addition to performance improvements, the authors demonstrate that $D$ is able to learn semantically-relevant features that are both explainable (via latent-space walk based validation) and usable (via feature-based supervised classification).  In fact, the extracted features from $D$ were so informative that they were able to discover associations between the input noise vector $Z$ and some features, and even modify the generated images (such as face rotation) using simple interpolation along the correct axis in $Z$-space.

%The strong semantic learning power offered by DCGAN made it a strong candidate for enabling full unsupervised learning tasks such that the features learned by $D$ can be later explained and applied for re-use.

%In Machine Learning, and especially Computer Vision, domain variance between training and test data has been a long standing challenge.  The domain of a data set can be explained as components of the distribution that are invariant to class label, but unique to the data set as a whole, in contrast to other similar data sets.  Ganin et al. recognized that an adversarial approach known as a Domain Adversarial Neural Network (DANN) could be used to help improve Domain Adaption (DA).  Their adversarial approach essentially minimizes the loss with respect to the basic classification task, and maximizes the loss with respect to an adversarial model trying to distinguish between the training domain and a test domain.

\subsubsection{GAN in Semantic Learning and Generation}
Within the theme of semantic learning and generation, several significant contributions were made during 2016 and 2017.  Pathak, Krahenbuhl, Donahue, Darrell, and Efros used an adversarial approach to inpaint (fill in missing portions of) images with large extents of missing pixel data \cite{pathakCVPR16context}.  Their architecture is based on an auto-encoder \cite{hinton2006reducing} combined with GAN.  In their approach, the encoder-decoder learns a semantic encoding based on the non-missing portions and attempts to reproduce a whole image based on that semantic encoding.  The `reconstruction loss' is defined in terms of distance ($L2$) from the filled area to the removed area. The encoder-decoder is regarded as $G$, and a new discriminator $D$ is trained to predict whether its input is a reconstructed output from $G$ or an original image.  Interestingly, and in contrast with \cite{mirza2014conditional}, the authors achieved better results when $G$, but not $D$, was conditioned with context information \footnote{The paper defines context information as the missing pixels which, if true, undermines the objective (any statement of success should be based on withholding the missing pixels from the architecture).  I have requested clarification on this from the author (17 Oct 2018).}.

Wu et al. took a somewhat similar approach and extended a variational autoencoder \cite{larsen2015autoencoding} within a 3-dimensional GAN architecture (3D-VAE-GAN) which learns to generate 3D images from 2D examples \cite{NIPS2016_6096}.

Luc, Couprie, Chintala and Verbeek applied a straightforward GAN approach to the task of semantic segmentation on images \cite{Luc2016SemanticSU}.  Their approach uses a Convolutional Neural Network (CNN) based generative model $G$ to learn a class label for each pixel in the image based on a ground-truth labeling (supervised), thereby creating a segmentation map of the input image.  The discriminative model $D$ takes a segmentation map and tries to classify it as being a ground truth map or a generated map.  
%While $D$'s objective function tries to maximize classification accuracy of the input segmentation map as being either ground truth or generated, $G$'s objective function tries to maximize pixel class labeling accuracy with respect to ground truth while also minimizing accuracy.

Ehsani, Mottaghi, and Farhadi used a GAN approach to address the related dual purpose task of semantically segmenting objects within an image and completing those objects that were occluded by other objects in the image \cite{ehsani2017segan}.

Reed et al. applied a GAN approach to the dual-task of (1) generating realistic images (2) from text-based descriptions \cite{reed2016generative}.  Essentially, they create $G$ by concatenating the input noise with an encoding of the text description and feed the result into a feed-forward CNN using fractional-striding\footnote{The paper claims this to be a de-convolutional network, but I presume it to mean a CNN using fractional striding to achieve up-sampling.}.  They create $D$ by downsampling with CNN layers until a 4x4 representation is achieved, concatenate the text encoding onto each of the 16 frames, and continue convolutions to achieve the binary discriminator output.  The learning objectives are consistent with \cite{NIPS2014_5423}.  However, since there are two sources of error (error associated with producing fake-looking images and error associated with producing real-looking images that do not match the description), their approach addresses the second source of error by augmenting the labeled data with real images having non-matching descriptions, which $D$ must learn to recognize.

@@

Another rich area of research that has greatly benefited from the GAN architecture is image translation.  Generally, image translation deals with the learning of a meaningful semantic representation of an image in one domain, and then generating an image with the same semantic representation from a different domain.  Isola, Zhu, Zhou, and Efros designed a solution that appears to generalize well across various domain pairs for this task \cite{isola2017image}.  Their architecture follows a U-Net auto-encoder architecture \cite{ronneberger2015u} with DCGAN constraints \cite{salimans2016improved}.  Further, similar to \cite{pathakCVPR16context}, they constrain $D$'s task to focusing on high-frequency semantic accuracy using learned image patch losses that are fed from skipped connections from encoder layers (PatchGAN), while leveraging an $L1$ term in $G$'s loss to ensure low-frequency accuracy.  A later paper from Liu, Breuel, and Kautz also displays impressive results \cite{NIPS2017_6672} in image translation.

@@

Bansal et al. tackle the task of video-to-video translation and achieve fairly convincing results with a hierarchical GAN approach (RecycleGAN) \cite{bansal2018recyclegan}.  Their approach does not require matched video pairs (between domains), but instead introduces loss terms related to reconstruction (accuracy in translating from domain A to domain B and back to domain A again), next frame prediction, and straightforward generative and aversarial losses.

@@

Like any powerful technology, there are significant security implications associated with GANs, both with respect to how they are implemented and how they are used.  Indeed, most of the papers involving GAN implementations for computer vision applications rely on the ability of generated image/video to fool a human observer as an important qualitative measure of success.  The use of deep learning as a tool for generating convincing, non-authentic video was put in the public eye when a toolset developed by deepfake \cite{deepfakes-faceswap} was used maliciously to produce pornographic video content with public personalities, and later by celebrity Jordan Peele as a public service announcement, warning of the dangers of the technology \cite{peeleDeepFakes}.

@@

This section will explore the broader topic of Adversarial Machine Learning (ML) and it's role in security and privacy.  Back in 2008, Barreno, Nelson, Joseph, and Tygar discussed some security implications of ML and proposed a taxonomy to identify and analyze different attacks \cite{barreno2010security}.  In the proposed taxonomy, an attack was to be identified in terms of \textit{Influence}, \textit{Security Violation}, and \textit{Specificity}.  \textit{Influence} is similar to the concept of attack surface, and refers to whether the attacker (a) can control training data to influence the model (causative) or (b) must exploit an existing model during test/classification (exploratory).  \textit{Security Violation} refers to whether the attacker's goal is to result in misclassification of inputs (integrity compromise) or in general performance degradation (model availability compromise).  Lastly, \textit{Specificity} refers to whether the attack is targeted at a particular instance (eg. a single input) or a wide class of instances (one or multiple modes).

@@

When ML methods are used as a tool in an adversarial context like security, robustness of the model to adversarial examples becomes a primary design objective.  Spam filtering and intrusion detection systems (IDS) are two classic examples wherein the design objective is to accurate classify messages or traffic as benign or malicious, while the attacker's objective is to design his/her malicious content to be classified as benign.  %This scenario depicts an \textit{exploratory}, \textit{integrity}, and \textit{specific} attack.

Spam filtering has a relatively rich history from an adversarial learning perspective.  Word-based Bayesian spam filters date back to 1998 \cite{sahami1998bayesian}, and the first `Bayes vs. Bayes' attack surfaced (in the public eye) in 2004 \cite{graham2004beat}.

@@

Shokri, Stronati, Song, and Shmatikov have demonstrated a methodology to determine whether a specific sample was included within the training set for a target model \cite{shokri2017membership}.  Given a specific data sample $x_?$ and a target model $M_t$, their paper shows how to create multiple `shadow' models with different (real or synthesized) data from that used to train $M_t$, obtain prediction responses from each of the shadow models that can be labeled as `in' or `out' depending on whether each sample was part of that shadow models training set, and then use the labeled response data to then train an attack model $M_a$.  $M_a$ achieves good performance in predicting whether black-box responses from $M_t$ are associated with training input (`in') or test input (`out').  The paper addresses the problem of simply assuming that higher-confidence responses corresponds to `in' data by the following methodology: (a) start running randomized data samples through $m_t$, (b) use a hill-climbing algorithm to search the sample space until a high-confidence response is obtained, (c) repeat a and b until asufficiently large set of data is obtained, then (d) sample from the obtained samples and split into training and test sets for each shadow model.  In this way, the distributions for `in' and `out' synthesized data are the same from a confidence perspective.

Similarly, Song, Ristenpart, and Shmatikov demonstrated several white- and black-box approaches to build covert channels into ML models for the purpose of extracting sensitive/proprietary training data.  In the attack scenario, the model provider and the training data owner may be different entities.  The data owner may not wish to reveal the training data to the model developer, but instead submit the data to a secure ML service broker that then trains and delivers the working model back to the data owner.  White-box methods generally include methods for steganographically encoding training data into model parametrics that would then be available for extraction by an attacker with white-box access to the completed model.  More interestingly, a `capacity abuse' attack was described that addresses the black-box scenario.  Essentially, the learning algorithm automatically augments the training data with chosen (by the attacker) data and labels that data with an encoding of the private training data.  The model learns to classify the original and malicious training data according to their labels, and then the attacker, having balack-box access to the model, can present the known malicious data to the model and the responses will be an encoding of the private training data.  I hypothesize that performance of the model for both it's benign purpose as well as it's covert purpose depends on the malicious data being sparse.  The intuition is that since sparse data is statistically distant from the private training data, it will not have adverse affects on classification; and since each sparse sample is distant from other sparse samples, they can result in higher accuracy predictions.  As a follow-up independent study, I demonstrated, under ideal conditions, that the Membership Inference \cite{shokri2017membership} methodology could be used to detect whether a given model was trained on a sparse distribution or not, thereby serving as a potential indicator of covert channel(s) \cite{stein2018covert}.

>>>>

%\subsection{Introduction}
The Generative Adversarial Nets (GAN) framework was first introduced by Goodfellow et al. in 2014 \cite{NIPS2014_5423}.  The GAN framework involves the simultaneous training of both a generative model $G$ with parameters $\theta_g$ and a discriminative model $D$ with parameters $\theta_d$.  Given a target data space $T$ with distribution $p_t$, $G$'s task is to learn a mapping from a noisy input $z$ to the data space $T$ ($G:Z \rightarrow G(z) \sim p_g \approx p_t$); while $D$'s task is to discriminate whether some input $x$ originated from either $T$ or $G(z)$ ($D: X \rightarrow \{0, 1\}$).  Since $G$ would like to generate samples that are representative of $T$, and therefore make $D$'s task more difficult by capturing $p_t$ with $p_g$, $G$ includes a loss term that is based on whether $D$ successfully discriminated inputs as $T$ or $G(z)$ and back-propagates $D$'s success as error to $\theta_g$ appropriately.  In this way, $G$ learns how to generate data that is hard for an ever-improving $D$ to distinguish.  Importantly, labeled data is not required for either $G$ or $D$ because the loss function used by $G$ is defined in terms of $D(x)$ and $(1-D(G(z))) \in \{0, 1\}$ (ie. did $G$ fool $D$?) and the labels for $x$ essentially map to $\{p_t, p_g\}$ (ie. from target or generated data?).  Thus, the GAN framework presents a promising approach for generating data that approximates a target distribution in an unsupervised manner.

@@

In the original GAN, $G$ learns to generate data that estimates $p_t$, but cannot target specific sub-distributions within $p_t$, such as class labels or modes within $p_t$.  Shortly after the original GAN was introduced, Mirza and Osindero introduced an extension called Conditional GAN \cite{mirza2014conditional} which addresses this need.  By adding a conditioning input layer to both models $G$ and $D$, one can present the conditioning data $y$ alongside the normal data.  $G$ will learn a mapping from $z$ to $X$ given $y$ that will result in making classification of $X$ given $y$ difficult for $D$.  This advancement seems obvious in retrospect, but warrants contemplation.  While $G$ represents a mapping that captures the distribution of the target data space $T$ in general, the noisy input $z$ can be regarded as the diversity component of the input and $y$ can regarded as the specification component of the input.  Since $y$ is constant within a given mode, a smaller portion of the overall networks for $G$ and $D$ can focus on the generation and discrimination, respectively, of the modal contribution whereas the remaining portions of the networks can focus on the unspecified contributions from $z$.  Of course, Conditional GAN requires that conditioning data (eg. labels) are available for all target samples $x \in X$.

Radford, Metz, and Chintala \cite{DBLP:journals/corr/RadfordMC15} evaluated various model architectures and recommended a set of guidelines and constraints for $G$ and $D$ architectures that appeared to perform well in terms of stability, convergence, resolution, and depth of representation.  These guidelines describe a Deep Convolutional GAN (DCGAN) and are summarized as follows: (a) use convolution and fractional convolution layers with striding to achieve adaptive down-sampling ($D$) or up-sampling ($G$), respectively, rather than fixed/deterministic methods (i.e. max pooling), (b) use batch normalization between convolution layers to mitigate collapse or failure due to poor initialization or vanishing gradients, (c) avoid fully-connected layers, with the exception of the input to $G$ and the output of $D$, to help earlier convergence, and (d) use Rectifier Linear Unit (ReLU) activation for input and hidden layers in $G$, tanh for the output layer in $G$, and Leaky ReLU for all layers in $D$.  In addition to performance improvements, the authors demonstrate that $D$ is able to learn semantically-relevant features that are both explainable (via latent-space walk based validation) and usable (via feature-based supervised classification).  In one case they were able to discover a linear vector in $Z$-space that could control rotation of faces.

\subsubsection{GAN in Semantic Learning and Generation}

Within the theme of semantic learning and generation, Pathak, Krahenbuhl, Donahue, Darrell, and Efros used an adversarial approach to inpaint (fill in missing portions of) images with large extents of missing pixel data \cite{pathakCVPR16context}.  Their architecture is based on an auto-encoder \cite{hinton2006reducing} combined with GAN.  In their approach, the encoder-decoder learns a semantic encoding based on the non-missing portions and attempts to reproduce a whole image based on that semantic encoding.  The `reconstruction loss' is defined in terms of distance ($L_2$) from the filled area to the removed area. The encoder-decoder is regarded as $G$, and a new discriminator $D$ is trained to predict whether its input is a reconstructed output from $G$ or an original image.  Interestingly, and in contrast with \cite{mirza2014conditional}, the authors achieved better results when $G$, but not $D$, was conditioned with context information \footnote{The paper defines context information as the missing pixels which, if true, undermines the objective (any statement of success should be based on withholding the missing pixels from the architecture).  I have requested clarification on this from the author (17 Oct 2018).}.

%Wu et al. took a somewhat similar approach and extended a variational autoencoder \cite{larsen2015autoencoding} within a 3-dimensional GAN architecture (3D-VAE-GAN) which learns to generate 3D images from 2D examples \cite{NIPS2016_6096}.

Luc, Couprie, Chintala and Verbeek applied a straightforward GAN approach to the task of semantic segmentation on images \cite{Luc2016SemanticSU}.  Their approach uses a Convolutional Neural Network (CNN) based generative model $G$ to learn a class label for each pixel in the image based on a ground-truth labeling (supervised), thereby creating a segmentation map of the input image.  $D$ then takes a segmentation map and tries to classify it as being a ground truth map or a generated map.  
%While $D$'s objective function tries to maximize classification accuracy of the input segmentation map as being either ground truth or generated, $G$'s objective function tries to maximize pixel class labeling accuracy with respect to ground truth while also minimizing accuracy.

%Ehsani, Mottaghi, and Farhadi used a GAN approach to address the related dual purpose task of semantically segmenting objects within an image and completing those objects that were occluded by other objects in the image \cite{ehsani2017segan}.

Reed et al. applied a GAN approach to the dual-task of (1) generating realistic images (2) from text-based descriptions \cite{reed2016generative}.  Essentially, they create $G$ by concatenating the input noise with an encoding of the text description and feed the result into a feed-forward CNN using fractional-striding\footnote{The paper claims this to be a de-convolutional network, but I presume it to mean a CNN using fractional striding to achieve up-sampling.}.  $D$ then down-samples with CNN layers until a 4x4 representation is achieved, concatenates the text encoding onto each of the 16 frames, and continues convolutions to achieve the binary discriminator output.  The learning objectives are consistent with \cite{NIPS2014_5423}.  However, since there are two sources of error (error associated with producing fake-looking images and error associated with producing real-looking images that do not match the description), their approach addresses the second source of error by augmenting the labeled data with real images having non-matching descriptions, which $D$ must learn to recognize.

@@

Another rich area of research that has greatly benefited from the GAN architecture is image translation.  Generally, image translation deals with the learning of a meaningful semantic representation of an image in one domain, and then generating an image with the same semantic representation from a different domain.  Isola, Zhu, Zhou, and Efros designed a solution that appears to generalize well across various domain pairs for this task \cite{isola2017image}.  Their architecture follows a U-Net auto-encoder architecture \cite{ronneberger2015u} with DCGAN constraints \cite{salimans2016improved}.  Further, similar to \cite{pathakCVPR16context}, they constrain $D$'s task to focusing on high-frequency semantic accuracy using learned image patch losses that are fed from skipped connections from encoder layers (PatchGAN), while leveraging an $L_1$ term in $G$'s loss to ensure low-frequency accuracy.  A later paper from Liu, Breuel, and Kautz also displays impressive results \cite{NIPS2017_6672} in image translation.

@@

%Bansal et al. tackle the task of video-to-video translation and achieve fairly convincing results with a hierarchical GAN approach (RecycleGAN) \cite{bansal2018recyclegan}.  Their approach does not require matched video pairs (between domains), but instead introduces loss terms related to reconstruction (accuracy in translating from domain A to domain B and back to domain A again), next frame prediction, and straightforward generative and aversarial losses.

@@

Like any powerful technology, there are significant security implications associated with GANs, both with respect to how they are implemented and how they are used.  Indeed, most of the papers involving GAN implementations for computer vision applications rely on the ability of generated image/video to fool a human observer as an important qualitative measure of success.  The use of deep learning as a tool for generating convincing, non-authentic video was put in the public eye when a tool set developed by deepfake \cite{deepfakes-faceswap} was used maliciously to produce pornographic video content with public personalities, and later by celebrity Jordan Peele as a public service announcement, warning of the dangers of misuse of the technology \cite{peeleDeepFakes}.

@@

This section will explore the broader topic of Adversarial Machine Learning (ML) and it's role in security and privacy.  In 2008, Barreno, Nelson, Joseph, and Tygar discussed some security implications of ML and proposed a taxonomy to identify and analyze different attacks \cite{barreno2010security}.  In the proposed taxonomy, an attack was to be identified in terms of \textit{Influence}, \textit{Security Violation}, and \textit{Specificity}.  \textit{Influence} is similar to the concept of attack surface, and refers to whether the attacker (a) can control training data to influence the model (causative) or (b) must exploit an existing model during test/classification (exploratory).  \textit{Security Violation} refers to whether the attacker's goal is to result in misclassification of inputs (integrity compromise) or in general performance degradation (model availability compromise).  Lastly, \textit{Specificity} refers to whether the attack is targeted at a particular instance (eg. a single input) or a wide class of instances (one or multiple modes).

@@

When ML methods are used as a tool in an adversarial context like security, robustness of the model to adversarial examples becomes a primary design objective.  Intrusion detection systems (IDS) and Spam filters are two classic examples wherein the design objective is to accurate classify messages or traffic as benign or malicious, while the attacker's objective is to design his/her malicious content to be classified as benign (i.e. evade detection).  %This scenario depicts an \textit{exploratory}, \textit{integrity}, and \textit{specific} attack.

Russu, Demontis, Biggio, Fumera, and Roli explore a formalization of the classification evasion problem and some principled reasoning toward the design of robustness in the context of linear models and kernels \cite{russu2016secure}.  Essentially, they formalize the attack paradigm as trying to transform a malicious input $x$ into a still-malicious input $x^\prime$ such that $x^\prime$ will be classified as benign and the distance (norm) between $x^\prime$ and $x$ is minimized.  They discuss different paradigms for sparse attacks, where the attacker would like to modify as few features as possible (eg. Spam), and dense attacks, where the attacker can make minimal modifications to a large number of features (such as image perturbations).  The paper provides proof, under the assumption that an attacker will try to minimize their $L_1$ distance (from $x^\prime$ to $x$) for sparse attacks and $L_2$ distance for dense attacks, that classifiers should use $L_{\infty}$ regularization and $L_2$ regularization on the parameters, respectively.  They extend the proof to non-linear kernels, resulting in recommendations of Laplacian kernels for sparse attacks, and Radial Basis Function for dense.  They did not extend their work to highly complex adversarial distance functions (like those from GANs), but it nevertheless provides a principled basis for the nature of the adversarial learning task.

Spam filtering is a very real example of this problem, and has a relatively rich history from an adversarial learning perspective.  Word-based Bayesian Spam filters date back to 1998 \cite{sahami1998bayesian}, and the first `Bayes vs. Bayes' attack surfaced (in the public eye) in 2004 \cite{graham2004beat}.  These early examples demonstrated the concept, but were not human-spoofable.  Generating adversarial perturbations that (a) retain the same general Spam content, (b) are not detectable by humans, and (c) result in classification evasion, has proved to be a difficult challenge.  Recently, Iyyer, Wieting, Gimpel, and Zettlemoyer developed an approach known as Syntactically Controlled Paraphrase Networks \cite{DBLP:journals/corr/abs-1804-06059}.  First, they implemented a parse generator which takes, as input, a sentence $s_1$, a full parse $p_1$ of $s_1$ (obtained using \cite{manning2014stanford}), and a target template $t_2$, and provides a target parse $p_2$.  Next, they implemented a paraphrase generator which takes, as input, $s_1$ and $p_2$, and generates a paraphrase sentence $s_2$.  They show that randomly generated paraphrase samples (not adversarially learned) result in a relatively high number of miss-classifications, and also that augmenting those classification models at train-time with these syntactically-diverse adversarial examples results in better performance in the face of new adversarial examples.

@@

Shokri, Stronati, Song, and Shmatikov have demonstrated a methodology to determine whether a specific sample was included within the training set for a target model \cite{shokri2017membership}.  Given a specific data sample $x_?$ and a target model $M_t$, their paper shows how to create multiple `shadow' models with different (real or synthesized) data from that used to train $M_t$, obtain prediction responses from each of the shadow models that can be labeled as `in' or `out' depending on whether each sample was part of that shadow models training set, and then use the labeled response data to train an attack model $M_a$.  After training, $M_a$ achieves good performance in predicting whether black-box responses from $M_t$ are associated with training input (`in') or test input (`out').  The paper addresses the issue of bias from confidence in the responses by synthesizing the data and sampling from the subset of that data that results in similar confidence distributions from $M_t$.

Similarly, Song, Ristenpart, and Shmatikov demonstrated several white- and black-box approaches to build covert channels into ML models for the purpose of extracting sensitive/proprietary training data.  In the attack scenario, the data owner may not wish to reveal the training data to the model developer, but rather have the model trained and delivered by a secure third part.  White-box methods were presented but, more interestingly, a `capacity abuse' attack was described that addresses the black-box scenario.  Essentially, the learning algorithm automatically augments the training data with chosen (by the attacker) data that is labeled with an encoding of the private training data.  The model learns on both the original and malicious training data, and then the attacker, having black-box access to the model, can present the known malicious data to the model and receive the encoded private data via the responses.  I hypothesized that performance of the model for both its benign purpose as well as its covert purpose depends on the malicious data being sparse.  The intuition is that since sparse data is distant  from the private training data (in the feature space), it will not have adverse affects on classification; and since each sparse sample is distant from other sparse samples, they are mutually separable resulting in higher accuracy predictions.  As a follow-up independent study, I demonstrated under ideal conditions that the Membership Inference \cite{shokri2017membership} methodology could be used to detect whether a given model was trained on a sparse distribution or not, thereby serving as a potential indicator of covert channel(s) \cite{stein2018covert}.

ML robustness in the face of adversarial examples is likely to continue being an open problem for some time.  The challenge is not a transient implementation issue that will be worked out as ML technology matures, but rather, like generalization, a core learning issue at the heart of the gap between ML and true intelligence.  In this vein, I feel that a deeper understanding of complex models, specifically deep learning networks, including properties, topographies, and structures, and their effects in adversarial scenarios.  For example, characterizing parameter evolution in the manifold during training on benign data sets vs data sets with adversarial augmentation may reveal indicators that could be measured directly on future models (in the absence of adversarial data).  Further, the formalized approach discussed in \cite{russu2016secure} could be extended to more complex networks.  Since knowledge of the adversary's perturbation minimization objective helped inform provable design guidelines for the classifier, perhaps a finer-grained approach to adversarial learning (eg. segmentation of large generative and classification networks with complex tasks into matched ensembles of smaller networks with simpler tasks) will help increase model robustness to adversarial examples.
